Open Software - Restricted Data:  A Suicide/Climate Case Study.

### 2015-11-04 report1_high_level/manuscript.Rmd
add Garnaut climate change scenarios to the PDF, add the PDF

---
title: 'Open Software - Restricted Data:  A Suicide/Climate Case Study.'
author:  
- name: Ivan C. Hanigan
  affilnum: 1
  email: ivan.hanigan@anu.edu.au  
- name: David Fisher
  affilnum: 2
- name: Steven McEachern
  affilnum: 3
affiliation:
- affilnum: 1
  affil: National Centre for Epidemiology and Population Health (ANU) 
- affilnum: 2
  affil: Information Technology Services (ANU)
- affilnum: 3
  affil: Australian Data Archives (ANU)
header-includes:
  - \usepackage{graphicx}
  - \usepackage{url}   
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    number_sections: yes
    template: components/manuscript.latex
  html_document: null
  word_document: null
fontsize: 11pt
capsize: normalsize
csl: meemodified.csl
documentclass: article
classoption: a4paper
spacing: singlespacing
linenumbers: no
bibliography: references.bib
abstract: no
---
<!--
%\VignetteEngine{knitr::rmarkdown}
%\VignetteIndexEntry{Example Manuscript}
-->
```{r, eval = F, echo = F}
library(rmarkdown)
library(knitr)
library(knitcitations)
library(bibtex)
cleanbib()
#rm("bib")
#options("cite_format"="pandoc")
cite_options(citation_format = "pandoc", check.entries=FALSE)

dir()
render("manuscript.Rmd", "pdf_document")
#browseURL("manuscript.pdf")
```
```{r, echo = F, results = 'hide'}
# load
if(!exists("bib")){
bib <- read.bibtex("~/references/library.bib")

@@

>>>>

---
title: 'Open Software - Restricted Data:  A Suicide/Climate Case Study.'
author:  
- name: Ivan C. Hanigan
  affilnum: 1
  email: ivan.hanigan@anu.edu.au  
- name: David Fisher
  affilnum: 2
- name: Steven McEachern
  affilnum: 3
affiliation:
- affilnum: 1
  affil: National Centre for Epidemiology and Population Health (ANU) 
- affilnum: 2
  affil: Information Technology Services (ANU)
- affilnum: 3
  affil: Australian Data Archives (ANU)
header-includes:
  - \usepackage{graphicx}
  - \usepackage{url}   
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    number_sections: yes
    template: components/manuscript.latex
  html_document: null
  word_document: null
fontsize: 11pt
capsize: normalsize
csl: meemodified.csl
documentclass: article
classoption: a4paper
spacing: singlespacing
linenumbers: no
bibliography: references.bib
abstract: no
---
<!--
%\VignetteEngine{knitr::rmarkdown}
%\VignetteIndexEntry{Example Manuscript}
-->
```{r, eval = F, echo = F}
setwd("~/projects/opensoftware-restricteddata.github.com/report1_high_level/")
library(rmarkdown)
library(knitr)
library(knitcitations)
library(bibtex)
cleanbib()
#rm("bib")
#options("cite_format"="pandoc")
cite_options(citation_format = "pandoc", check.entries=FALSE)

dir()
render("manuscript.Rmd", "pdf_document")
browseURL("manuscript.pdf")
```
```{r, echo = F, results = 'hide'}
# load
if(!exists("bib")){
bib <- read.bibtex("~/references/library.bib")

@@

```{r, eval = F, echo = F}
dir()
dir("~/data")
indir <- "~/data/GARNAUT mental health archive/1 Data/Rain"
dir(indir, pattern = "jpg")
filelist  <- c("A1BDRY_RainSD07.jpg",             "A1BWET_RainSD07.jpg"            )
for(fi in filelist){
  #file.copy(file.path(indir, fi), fi)
  txt <- sprintf("\\begin{figure}[!h]
\\centering
\\includegraphics[width=\\textwidth]{%s}
\\caption{%s}
\\label{fig:%s}
\\end{figure}
", fi, fi, fi)
  cat(txt)
}
```

## The Garnaut review climate change scenarios

\begin{figure}[!h]
\centering
\includegraphics[width=\textwidth]{A1BDRY_RainSD07.jpg}
\caption{A1BDRY RainSD07}
\label{fig:A1BDRYRainSD07}
\end{figure}

\begin{figure}[!h]
\centering
\includegraphics[width=\textwidth]{A1BWET_RainSD07.jpg}
\caption{A1BWET RainSD07}
\label{fig:A1BWET-RainSD07}
\end{figure}
